---
title: "Model Validation Assignment"
author: "sabina jamarkattel"
date: "2/2/2021"
output: word_document
---
 
```{r}
library(tidyselect)
library(tidymodels)
library(lubridate)
```
```{r}

bike<-bike_cleaned_2 <- read_csv("C:/Users/Sabina/Desktop/BAN502 PREDICTIVE ANALYTICS/MODULE 3/ASSIGNMNET 1/bike_cleaned-2.csv")
bike = bike %>% mutate(dteday = mdy(dteday)) 
bike = bike %>% mutate_if(is.character,as.factor)
bike = bike %>% mutate(hr = as.factor(hr))
str(bike)

```
# Task 1
```{r}
set.seed(1234)
bike_split = initial_split(bike, prob = 0.70, strata = count)
train = training(bike_split)
test = testing(bike_split)

```

# Task 2
#  How many rows of data are in each set :- Train has 13036 rows and Test has 4343 rows.
 


 # Task 3 
```{r}
bike_recipe = recipe(count ~ season +hr+holiday+weekday+temp+mnth+weathersit ,  train)

lm_model = 
  linear_reg() %>% 
  set_engine("lm")

lm_wflow = 
  workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(bike_recipe)

lm_fit = fit(lm_wflow, train)
```
```{r}
summary(lm_fit$fit$fit$fit)
```
# The Adjusted R-squared value is 0.0622.


#Task 4
```{r}
predict_train = predict(lm_fit,train)

ggplot(predict_train ,aes(x=.pred)) +
geom_histogram() +
  theme_bw()

```
# FRom the histogram above we can see that, the value of variable .pred between 0-300 is more concentrated and also the maximum count  is around 300.



#Task5
```{r}
lm_fit %>% predict(test) %>% bind_cols(test) %>% metrics(truth = count, estimate = ".pred")
```


# Perfomance on the test set is similar to that on the training set.So,this suggests that there is not much difference in the R-squared value and our model is not overfitting,hence making a good model.